---
title: "Live portfolio"
output: html_document
---

This document shows the results of the current live portfolio. 

## Current strategy

Think of portfolio as 3 different funds

Retirement: IRA + Defferred Comp + 401K = Bonds
MCO Stock: Stock
Liquid Stock: Regular portfolio

Will over time go back to optimizing whole portfolio.

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
library(knitr)
```

```{r, echo=FALSE, results="hide"}

#devtools::install_github("joshuaulrich/quantmod", ref="157_yahoo_502")
#remotes::install_github("joshuaulrich/quantmod", ref="157_yahoo_502")

#setInternet2(TRUE)
con = gzcon(url('https://github.com/systematicinvestor/SIT/raw/master/sit.gz', 'rb'))
source(con)
close(con)

load.packages('quantmod')   

tickers = spl('
              TLT = TLT + VUSTX,
#              TLT = BLV + VBLTX,
             BLV = BLV + VBLTX,
              GLD = GLD + GOLD,
#              GLD = GLD,
              SPY = SPY + VFINX,
#              SHY = SHY + VFISX,
              SHY = VFISX,
              VEU = VEU + FDIVX,
              MCO
              ')

 tickers1 = spl('
               TLT,
               VUSTX,
               BLV,
               VBLTX,
               GLD,
               SPY,
               VFINX,
               SHY,
               VFISX,
               VEU,
               FDIVX,
               MCO
               ')
 
 # Use external data
raw <- new.env()


getSymbols.extra(tickers1, src='yahoo', from = '1970-01-01', env = raw, set.symbolnames = T, auto.assign = T)
for(i in raw$symbolnames) raw[[i]] = adjustOHLC(raw[[i]], use.Adjusted = FALSE, symbol.name=i)
raw$GOLD = bundes.bank.data.gold()

# How to make BLV replace TLT as of 1st March?
# What if we use TLT as the signal, but trade BLV?

equities.2 = spl("SPY,VEU")

data <- new.env()

#getSymbols(tickers1, src='yahoo', from = '1970-01-01', env = data)
getSymbols.extra(tickers, src = 'yahoo', from = '1970-01-01', env = data, set.symbolnames = T,raw.data = raw, auto.assign = T)
#getSymbols.extra(tickers, src = 'google', from = '1970-01-01', env = data, set.symbolnames = T,raw.data = raw.data, auto.assign = T)
#for(i in data$symbolnames) data[[i]] = adjustOHLC(data[[i]], use.Adjusted=T)
#for(i in data$symbolnames) data[[i]] = adjustOHLC(data[[i]], use.Adjusted = FALSE, symbol.name=i)


bt.prep(data, align='remove.na')


#*****************************************************************
# Setup
#****************************************************************** 		
prices = data$prices   
n = ncol(prices)
nperiods = nrow(prices)

#period.ends = endpoints(prices, 'quarters')
period.ends = endpoints(prices, 'months')
#period.ends = endpoints(prices, 'days')
period.ends = period.ends[period.ends > 0]		
period.ends = c(1, period.ends)



models = list()


# SPY Buy and Hold
data$weight[] = NA
data$weight$SHY=0
data$weight$SPY=1
data$weight$TLT=0
data$weight$GLD=0
data$weight$MCO=0
data$weight$BLV=0


models$spy.bh = bt.run.share(data, trade.summary=T, clean.signal=F)

# Equal Weight
data$weight[] = NA
data$weight$SHY=0
data$weight$MCO=0
data$weight$SPY=1/3
data$weight$TLT=1/3
data$weight$GLD=1/3
data$weight$BLV=0

models$equal.weight = bt.run.share(data, trade.summary=T, clean.signal=F)

# Target asset volatility

max.leverage = 4

ret = bt.apply.matrix(prices, ROC, type='discrete')
abs.ret = abs(ret)
abs.ret.average = bt.apply.matrix(abs.ret, SMA, 30)
#abs.ret.average = bt.apply.matrix(abs.ret, SMA, 60)

leverage = 1/(abs.ret.average^2)

days = 252
sma = bt.apply.matrix(prices, SMA, days )
annual.ret = prices/mlag(prices,days )
annual.ret.lev = annual.ret * leverage
absmom = annual.ret - c(coredata(annual.ret$SHY))


leverage$SHY = 0
positions = (((prices > sma)*0.5)+ ((absmom >0) * 0.5))

price.div.sma = prices/sma


# 
positions$SHY = 0
positions$MCO = 0

# Positions BLV before 1st March 2017 = 0
# Positions TLT after 1st March 2017 = 0
positions$BLV["/2017-03-01"] = 0
positions$TLT["2017-03-01/"] = 0 




top.assets = ntop(annual.ret[,equities.2],1) 

positions$VEU = 0

portfolio.weight = positions*leverage
#portfolio.weight[,equities.2]=portfolio.weight[,equities.2]*top.assets

max.weight = max(rowSums(portfolio.weight[period.ends,]),na.rm=TRUE)




overall.leverage = 9/max.weight
#overall.leverage = 5/max.weight

portfolio.weight = portfolio.weight * drop(overall.leverage)

lev.cap = iif(rowSums(portfolio.weight)>max.leverage, max.leverage/rowSums(portfolio.weight), 1)

portfolio.weight = portfolio.weight * lev.cap

data$weight[] = NA
data$weight[period.ends,] = portfolio.weight[period.ends,]
models$equalassetvol.equalportvol.pos = bt.run.share(data, trade.summary=T, clean.signal=F)

#Calculate the rolling 12 month positive returns
models$equalassetvol.equalportvol.pos$equity=models$equalassetvol.equalportvol.pos$equity["1995-11-30/"]
twelve.ret = ROC(models$equalassetvol.equalportvol.pos$equity,252,type="discrete")
rolling.rets = (sum(twelve.ret > 0,na.rm=TRUE)/(sum(twelve.ret > 0,na.rm=TRUE)+sum(twelve.ret < 0,na.rm=TRUE)))*100

```

## SMA

```{r, echo=FALSE}
#kable(tail(price.div.sma,10))
kable(tail(data.frame(Date=index(price.div.sma), coredata(price.div.sma)),10), format.args = list(big.mark = ","))
```

## ABSMom

```{r, echo=FALSE}
#kable(tail(absmom,10))
kable(tail(data.frame(Date=index(absmom), coredata(absmom)),10), format.args = list(big.mark = ","))
```

## Volatility 

```{r, echo=FALSE}
kable(tail(data.frame(Date=index(abs.ret.average[period.ends,]), coredata(abs.ret.average[period.ends,])),10), format.args = list(big.mark = ","))
```

## Trades

```{r, echo=FALSE}
kable(tail(models$equalassetvol.equalportvol.pos$trade.summary$trades,10))
```

## Ideal portfolio weights

```{r, echo=FALSE}

kable(tail(data.frame(Date=index(portfolio.weight[period.ends,]), coredata(portfolio.weight[period.ends,])),10))
```


## Transition map 

```{r, echo=FALSE}
plotbt.transition.map(models$equalassetvol.equalportvol.pos$weight)
```

## System details

```{r, echo=FALSE}
model.detail = list()

model.detail = bt.detail.summary(models$equalassetvol.equalportvol.pos)
model.detail$System$Roll.TwelveM = (sum(twelve.ret > 0,na.rm=TRUE)/(sum(twelve.ret > 0,na.rm=TRUE)+sum(twelve.ret < 0,na.rm=TRUE)))*100
kable(list2matrix(model.detail))
max.drawdown = compute.max.drawdown(models$equalassetvol.equalportvol.pos$equity)
```



## Monthly performance

```{r, echo=FALSE, results="hide"}
plotbt.monthly.table(models$equalassetvol.equalportvol.pos$equity)
```

## Weights

```{r, echo=FALSE}
kable(last(models$equalassetvol.equalportvol.pos$weight))
```


```{r, echo=FALSE, results="hide"}

TradesFile = read.csv("../Trades.csv", stringsAsFactors=FALSE, header=F)


# Build a structure of accounts
# Load each data column into it's account

accounts=list()


#Create a data frame with the Trade Dates, column name date
TradeDates = TradesFile[1][c(-1,-2),]

for(i in 2:ncol(TradesFile)){
  
  column.name = TradesFile[2,i]
  account.name = TradesFile[1,i]
  if(account.name %in% names(accounts)){
    
    accounts[[account.name]][[column.name]]=as.numeric(TradesFile[i][c(-1,-2),])
  } else {
    
    accounts[[account.name]]=list()
    accounts[[account.name]][["date"]]=TradeDates
    accounts[[account.name]][[column.name]]=as.numeric(TradesFile[i][c(-1,-2),])
  }
}

# Tax the Restricted Units
accounts$`Restriced Units`$MCO = accounts$`Restriced Units`$MCO * 0.6

# Calculate the volatility of MCO

mco = prices$MCO
mco.ret = bt.apply.matrix(mco, ROC, type='discrete')
mco.abs.ret = abs(mco.ret)
mco.ret.average = bt.apply.matrix(mco.abs.ret, SMA, 60)
mco.vol = mco.ret.average/abs.ret.average$SPY

prices$Cash = 1
prices$SPYX = prices$SPY*(94.410/237.81)

framify <- function(x){ 
  dd = as.data.frame(matrix(unlist(x), nrow=length(unlist(x[1]))))
  colnames(dd)=names(x)
  return (dd)
}

accounts.dfs = lapply(accounts, framify)

last.prices = last(prices)
# Now make the dataframes into xts objects
# accounts.xts = lapply(accounts.dfs, function(x){xts(x,order.by=index(last.prices))})
account.dates = as.Date(accounts.dfs$FolioFn$date,format="%m/%d/%Y")
accounts.xts = lapply(accounts.dfs, function(x){xts(x,order.by=account.dates)})

prices$dummy = 1
account.prices = prices[paste((min(account.dates)),"/")]


value.accounts = function(x){
  nm=names(x[,-1])
  x =merge(account.prices$dummy,x)
  x = na.locf(x)
  x=x[,nm]
  values = account.prices[,nm]*x
  values$dummy = 0
  values$sum = rowSums(values)
  return(values)
}

accounts.value = lapply(accounts.xts,value.accounts)


account.names = names(accounts.value)
account.summary = accounts.value[[1]]$sum

for(i in 2:length(accounts.value)){
   account.summary = cbind(account.summary,accounts.value[[i]]$sum)
}

names(account.summary)=account.names
account.summary$networth = rowSums(account.summary)

tail(account.summary)
```

### Networth monthly 

```{r, echo=FALSE, results="hide"}
plotbt.monthly.table(account.summary$networth)
#plot(account.summary$networth)
```

```{r, echo=FALSE, results="hide"}
# Need to calculate the amount of equities, gold and bonds to work out the trades




# 
# account.summary = prices$dummy
# 
# summarize.accounts<-function(x){
#   account.summary= merge(account.summary,x$sum)
# }
# 
# accounts.value = lapply(accounts.value,summarize.accounts)
# 
# 
# 
# # 
# # accounts.value = lapply(accounts.xts, function(x){(x*last.prices)} )
# 
# # Get the last weights and exposures
# 
last.portfolio.weights =last(models$equalassetvol.equalportvol.pos$weight)
current.mco.vol = last(mco.vol)
last.accounts.value = last(account.summary)
# 

liquid.funds = last.accounts.value$IB
min.liquid.funds = 1000000

#max.exposure = (liquid.funds - min.liquid.funds)/abs(max.drawdown)

max.exposure = liquid.funds

 trade.values = list()
 trade.values$TLT = last.portfolio.weights$TLT*max.exposure
 trade.values$BLV = last.portfolio.weights$BLV*max.exposure
 trade.values$GLD = last.portfolio.weights$GLD*max.exposure
 trade.values$SPY = last.portfolio.weights$SPY*max.exposure
 trade.values$VEU = last.portfolio.weights$VEU*max.exposure

# 
 shares = list()
 shares$TLT = as.integer(last(accounts.xts$IB$TLT)) 
 shares$BLV = as.integer(last(accounts.xts$IB$BLV)) 
 shares$GLD = as.integer(last(accounts.xts$IB$GLD))
 shares$SPY = as.integer(last(accounts.xts$IB$SPY))
 shares$VEU = as.integer(last(accounts.xts$IB$VEU))
 
#Current exposures - total exposures to bonds, equities and gold
 current.exposure = list()
 current.exposure$TLT = shares$TLT*last(prices$TLT)
 current.exposure$BLV = shares$BLV*last(prices$BLV)
 current.exposure$GLD = shares$GLD*last(prices$GLD)
 current.exposure$SPY = shares$SPY*last(prices$SPY)
 current.exposure$VEU = shares$VEU*last(prices$VEU)
 
next.portfolio.weights =last(portfolio.weight[period.ends,])

#Target Exposures 
target.exposure=list()
target.exposure$TLT = next.portfolio.weights$TLT*max.exposure
target.exposure$BLV = next.portfolio.weights$BLV*max.exposure
target.exposure$GLD = next.portfolio.weights$GLD*max.exposure
target.exposure$SPY = next.portfolio.weights$SPY*max.exposure
target.exposure$VEU = next.portfolio.weights$VEU*max.exposure

#Target IB Exposures 
next.trade.values=list()
next.trade.values$TLT = next.portfolio.weights$TLT*max.exposure
next.trade.values$BLV = next.portfolio.weights$BLV*max.exposure
next.trade.values$GLD = next.portfolio.weights$GLD*max.exposure
next.trade.values$SPY = next.portfolio.weights$SPY*max.exposure
next.trade.values$VEU = next.portfolio.weights$VEU*max.exposure

#Target shares
next.shares = list()
next.shares$TLT = as.integer(next.trade.values$TLT/last(prices$TLT))
next.shares$BLV = as.integer(next.trade.values$BLV/last(prices$BLV))
next.shares$GLD = as.integer(next.trade.values$GLD/last(prices$GLD))
next.shares$SPY = as.integer(next.trade.values$SPY/last(prices$SPY))
next.shares$VEU = as.integer(next.trade.values$VEU/last(prices$VEU))

# Trade to make 

next.trade = list()
next.trade$TLT = next.shares$TLT - as.integer(last(accounts.xts$IB$TLT)) 
next.trade$BLV = next.shares$BLV - as.integer(last(accounts.xts$IB$BLV)) 
next.trade$GLD = next.shares$GLD - as.integer(last(accounts.xts$IB$GLD))
next.trade$SPY = next.shares$SPY - as.integer(last(accounts.xts$IB$SPY))
next.trade$VEU = next.shares$VEU - as.integer(last(accounts.xts$IB$VEU))
```

Given liquid equity of `r as.integer(liquid.funds)` a maximum exposure of `r as.integer(max.exposure)` is recommended. 

## Porfolio Weights

```{r, echo=FALSE}
kable(tail(models$equalassetvol.equalportvol.pos$weight,10))
```

## Current Overall Exposures

```{r, echo=FALSE}
expmat = list2matrix(current.exposure)
colnames(expmat) = "Exposure" 
kable(expmat, format.args = list(big.mark = ","))
```

## Target Overall Exposures (1st Month)

```{r, echo=FALSE}
expmat = list2matrix(target.exposure)
colnames(expmat) = "Exposure" 
kable(expmat, format.args = list(big.mark = ","))
```

## Current Ideal IB Exposures

```{r, echo=FALSE}
expmat = list2matrix(trade.values)
colnames(expmat) = "Exposure" 
kable(expmat, format.args = list(big.mark = ","))
```

## Target IB Exposures (1st Month)
```{r, echo=FALSE}
expmat = list2matrix(next.trade.values)
colnames(expmat) = "Exposure" 
kable(expmat, format.args = list(big.mark = ","))
```

## Current IB Shares

```{r, echo=FALSE}
sharesmat = list2matrix(shares)
colnames(sharesmat) = "Shares" 
kable(sharesmat, format.args = list(big.mark = ","))
```

## Target IB Shares (1st Month)
```{r, echo=FALSE}
sharesmat = list2matrix(next.shares)
colnames(sharesmat) = "Shares" 
kable(sharesmat, format.args = list(big.mark = ","))
```

## Next trade to make to rebalance (1st Month)

```{r, echo=FALSE}
trademat = list2matrix(next.trade)
colnames(trademat ) = "Shares" 
kable(trademat, format.args = list(big.mark = ","))
```

## Change in networth

```{r, echo=FALSE}
kable(tail(data.frame(Date=index(account.summary), coredata(account.summary)),2),digits = 0, format.args = list(big.mark = ","))
```